### 2018-07-29 FS/overview.tex
NIL

\documentclass{article}
\usepackage{xeCJK}
\usepackage{hyperref}
\title{Overview}
\date{}
\begin{document}

\maketitle

\tableofcontents
\newpage
\part{环境配置}
\section{虚拟机}
\begin{itemize}
\item \href{https://www.howtogeek.com/117635/how-to-install-kvm-and-create-virtual-machines-on-ubuntu/}{Installing qemu-kvm}

\end{itemize}
\section{GlusterFS}

\end{document}

### 2018-08-19 FS/overview.tex
8.19

@@
 \usepackage{hyperref}
+\usepackage{listings}
+\lstset{
+ columns=fixed,       
+ numbers=left,                                        % 在左侧显示行号
+ numberstyle=\tiny\color{gray},                       % 设定行号格式
+ frame=single,                                          % 不显示背景边框
+ keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
+ numberstyle=\footnotesize\color{darkgray},           
+ commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
+ stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
+ showstringspaces=false,                              % 不显示字符串中的空格
+ language=c++,                                        % 设置语言
+}
+
 \title{Overview}
@@
 \section{虚拟机}
+\begin{enumerate}
+\item \href{https://blogs.oracle.com/scoter/networking-in-virtualbox-v2}{VirtualBox Networking Configuration}
 \begin{itemize}
-\item \href{https://www.howtogeek.com/117635/how-to-install-kvm-and-create-virtual-machines-on-ubuntu/}{Installing qemu-kvm}
+\item Network Address Translation.
+\item Bridged Network.
+\item Internal Network.
+\item Host-only Networking.
+\item Port-forwarding.
+\end{itemize}
+\end{enumerate}
+\section{VirtualBox+Centos7+GlusterFS}
+\subsection{\href{https://docs.gluster.org/en/latest/Install-Guide/Common\_criteria/}{基本概念}}
+\begin{itemize}
+\item \textbf{trusted pool}:hosts
+\item \textbf{node}:server
+\item \textbf{brick}:device(filesystem)
+\item \textbf{export}:mount path of the bricks on a server
+\item \textbf{Gluster Volumn(Global Namespace)}:collection of bricks
+\item \textbf{GNFS and kNFS}:GNFS=inline NFS server. kNFS=kernel NFS. \href{https://en.wikipedia.org/wiki/Network\_File\_System}{NFS wiki}
+\item \textbf{DNS setup}:????
+\end{itemize}
 
-\end{itemize}
+\subsection{\href{https://wiki.centos.org/SpecialInterestGroup/Storage/gluster-Quickstart}{Installing GlusterFS on CentOs}}
+\begin{enumerate}
+\item Step 1: nodes.
+\item Step 2: \href{https://gluster-documentations.readthedocs.io/en/latest/Administrator\%20Guide/Setting\%20Up\%20Volumes/}{Format and mount the bricks.}
+\item Step 3: Installing glusterFS.
+\item Step 4: \href{https://wiki.centos.org/HowTos/Network/IPTables}{Configure iptables.}
+\item Step 5: \href{https://docs.gluster.org/en/v3/Administrator\%20Guide/Storage\%20Pools/}{Manage Trusted Storage Pool}
+\item Step 6: \href{https://gluster-documentations.readthedocs.io/en/latest/Administrator\%20Guide/Setting\%20Up\%20Volumes/}{Set up a GlusterFS Volume.}
+\end{enumerate}
+\part{GlusterFS开发}
+\href{https://docs.gluster.org/en/latest/Developer-guide/Developers-Index/\#contributing-to-the-gluster-community}{官方开发文档}
+\section{Workflow}
+\subsection*{\href{https://github.com/gluster/glusterfs}{Git}}
+\subsection*{\href{review.gluster.org}{Gerrit}}
+Code Review System.
+
+%\subsubsection{\href{https://docs.gluster.org/en/latest/Install-Guide/compiling-rpms/}{如何编译GlusterFS}}
+
+\part{文献}
 \section{GlusterFS}
-
 \end{document}

### 2018-08-23 NDP/NDP.tex
8.23

--- 2018-07-29 FS/overview.tex
@@
 \documentclass{article}
+\usepackage{amsmath}
+\usepackage{pdfpages}
 \usepackage{xeCJK}
 \usepackage{hyperref}
-\title{Overview}
+\usepackage{listings}
+\lstset{
+ columns=fixed,       
+ numbers=left,                                        % 在左侧显示行号
+ numberstyle=\tiny\color{gray},                       % 设定行号格式
+ frame=single,                                          % 不显示背景边框
+ keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
+ numberstyle=\footnotesize\color{darkgray},           
+ commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
+ stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
+ showstringspaces=false,                              % 不显示字符串中的空格
+ language=c++,                                        % 设置语言
+}
+\newcommand{\page}[2]{\hyperlink{#1.pdf.#2}{link}}
+
+\title{Near-Data Processing}
 \date{}
@@
 \newpage
-\part{环境配置}
-\section{虚拟机}
-\begin{itemize}
-\item \href{https://www.howtogeek.com/117635/how-to-install-kvm-and-create-virtual-machines-on-ubuntu/}{Installing qemu-kvm}
+\part{文献}
 
-\end{itemize}
-\section{GlusterFS}
-
+%\includepdf[pages=-]{.pdf}
 \end{document}

### 2018-08-26 NDP/NDP.tex
8.26

@@
 }
-\newcommand{\page}[2]{\hyperlink{#1.pdf.#2}{link}}
+\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
+\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}
 
 \title{Near-Data Processing}
+\author{陈辉}
 \date{}
 \begin{document}
-
 \maketitle
-
 \tableofcontents
@@
 \part{文献}
+\section{\textit{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}}
+\paper{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}{1}
+\section{\textit{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}}
+\paper{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}{1}
+\section{\textit{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}}
+See paper\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}{1}
+See presentation\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation)}{1}
 
-%\includepdf[pages=-]{.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation).pdf}
+
+%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
+%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}
+
 \end{document}

### 2018-08-27 AI/EC.tex
8.27

--- 2018-08-23 NDP/NDP.tex
@@
 }
-\newcommand{\page}[2]{\hyperlink{#1.pdf.#2}{link}}
+\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
+\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}
 
-\title{Near-Data Processing}
+\title{Evolutionary Computing and Machine Learning}
+\author{陈辉}
 \date{}
 \begin{document}
-
 \maketitle
-
 \tableofcontents
@@
 \part{文献}
+\section{\textit{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}}
+\paper{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}{1}
 
-%\includepdf[pages=-]{.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
+%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
+%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}
+
 \end{document}

### 2018-08-29 AI/EC.tex
8.29

@@
 \part{文献}
+\section{\textit{Population-Based-Training-of-Neural-Networks}}
+\paper{Population-Based-Training-of-Neural-Networks}{1}
+\subsection{Introduction}
+\paragraph{Keypoints of The Problem}
+
+\begin{itemize}
+		\item Hyperparameters tuning is essential.
+		\href{https://en.wikipedia.org/wiki/Hyperparameter\_optimization}{Wiki}.
+		\item Non-stationary problems might lead to non-stationary hyperparameters.
+		\item Tow main tuning tracks:
+\begin{itemize}
+		\item Parallel search. 
+		\item Sequential search.
+\end{itemize}
+\end{itemize}
+
+\paragraph{Brief Introduction to PBT}
+\paragraph{What PBT can do}
+
+\subsection{Related Work}
+
 \section{\textit{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}}
@@
 
+\includepdf[link=true,pages=-,fitpaper]{./papers/Population-Based-Training-of-Neural-Networks.pdf}
 \includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}

### 2018-09-01 AI/EC.tex

@@
 \subsection{Related Work}
+\paragraph{Bayesian optimisation framework}
+\paragraph{Main thoughts of PBT for training}A misture way: Parameters are more likely to be trained(partially) in standard way, while the hyperparameters are evolved(relatively slowly).
+
+\subsection{Population Based Training}
+\paragraph{Main idea}
+\begin{itemize}
+\item Training with a population that each member has different parameters and hyper parameters.
+\item In each iteration, a member takes steps and offer its weights, hyperparameters and evaluation. This is the main \textbf{communication} among members.
+\item Each member \textbf{\textit{exploit}} the best weights and hyperparameters among the whole polulation, then \textbf{\textit{explore}} new branches for next step.
+\end{itemize}
+\textbf{Remark. }Can we treat objective function as a \textbf{hyperparameter} too?\\
+e.g. With the improvement of models, can we eventually decrease the size of the batches for evaluation computing?\\
+
+\subsection{Experiments}
+\subsubsection{Deep Reinforcement Learning}
+
+\subsubsection{Machine Translation}
+
+\section{\textit{Evolution Strategies as a Scalable Alternative to Reinforcement Learning}}
+\book{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}{1}\\
+\textbf{Remark. }Someone pointed out that this paper is similar to \href{https://en.wikipedia.org/wiki/Simultaneous\_perturbation\_stochastic\_approximation}{SPSA}
 
@@
 \includepdf[link=true,pages=-,fitpaper]{./papers/Population-Based-Training-of-Neural-Networks.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning.pdf}
 \includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}

### 2018-09-05 NDP/NDP.tex
8.27
9.5

@@
 \documentclass{article}
+\usepackage{verbatim}
 \usepackage{amsmath}
@@
 \part{文献}
-\section{\textit{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}}
-\paper{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}{1}
-\section{\textit{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}}
-\paper{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}{1}
+\section{\textit{Cloud-Scale-Acceleration-Architecture}}
+\paper{Cloud-Scale-Acceleration-Architecture}{1}
+\subsection{Introduction}
+\textbf{Balance of Homogeneity and Specialization}\par
+Specialized accelerator should be programmable to adjust the diversity of cloud servers and rapid change. That's why we need FPGAs or GPUs.\\
+
+This paper describes a cloud-scale FPGA-based acceleration architecture called \textit{Configurable Cloud} which allows datapath of cloud communication to be accelerated with FPGAs.
+This datapath can include networking flows, \textbf{storage flows}, security operations and distributed applications.\\
+
+We use a protocol called \textbf{LTL(Lightweight Transport Layer)} to make the remote FPGA resources apper closer than either a single local SSD access or the time to get through the host's networking stack.\\
+
+\subsection{Hardware Architecture}
+\textbf{Designing Requirements}
+\begin{itemize}
+\item Homogeneity.
+\item Fungibility.
+\item Flexibility.
+
+\begin{itemize}
+\item \textit{Local compute acceleration(through PCIe)}.
+Local acceleration handles \textbf{hight-value scenarios} such as search rankingon each FPGA's host. 
+\item \textit{Network acceleration.} 
+e.g. intrusion detection, deep packet inspection and network encryption.
+\item \textit{Global application acceleration(through FPGA pools)}. Through this, idle FPGAs can be used for distributed large-scale applications such as machine learning.
+\end{itemize}
+
+\item \textbf{Physical restrictions}. e.g. physical space, power consumption, and temperature. That's \textbf{why we choose FPGAs instead of GPUs}.
+\end{itemize}
+
 \section{\textit{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}}
@@
 
-\includepdf[link=true,pages=-,fitpaper]{./papers/Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning.pdf}
-\includepdf[link=true,pages=-,fitpaper]{./papers/NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING.pdf}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Cloud-Scale-Acceleration-Architecture.pdf}
 \includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks.pdf}
-\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation).pdf}
-
 %\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}

### 2018-09-12 Templates/test/p.tex
9.12

              
\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\title[Your Short Title]{Your Presentation}
\author{You}
\institute{Where You're From}
\date{Date of Presentation}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% Uncomment these lines for an automatically generated outline.
%\begin{frame}{Outline}
%  \tableofcontents
%\end{frame}

\section{Introduction}

\begin{frame}{Introduction}

\begin{itemize}
  \item Your introduction goes here!
  \item Use \texttt{itemize} to organize your main points.
\end{itemize}

\vskip 1cm

\begin{block}{Examples}
Some examples of commonly used commands and features are included, to help you get started.
\end{block}

\end{frame}

\section{Some \LaTeX{} Examples}

\subsection{Tables and Figures}

\begin{frame}{Tables and Figures}

\begin{itemize}
\item Use \texttt{tabular} for basic tables --- see Table~\ref{tab:widgets}, for example.
\item You can upload a figure (JPEG, PNG or PDF) using the files menu. 
\item To include it in your document, use the \texttt{includegraphics} command (see the comment below in the source code).
\end{itemize}

% Commands to include a figure:
%\begin{figure}
%\includegraphics[width=\textwidth]{your-figure's-file-name}
%\caption{\label{fig:your-figure}Caption goes here.}
%\end{figure}

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\end{frame}

\subsection{Mathematics}

\begin{frame}{Readable Mathematics}

Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

\end{frame}

\end{document}

### 2018-09-13 FS/background/log.tex
9.13

--- 2018-08-23 NDP/NDP.tex
@@
 \usepackage{pdfpages}
+\usepackage{verbatim}
 \usepackage{xeCJK}
@@
 }
-\newcommand{\page}[2]{\hyperlink{#1.pdf.#2}{link}}
+\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
+\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}
 
-\title{Near-Data Processing}
+\title{Log Analysis}
+\author{陈辉}
 \date{}
 \begin{document}
-
 \maketitle
-
 \tableofcontents
 \newpage
-\part{文献}
+\section{The Log: What every software engineer should know about real-time data's unifying abstraction}
+\href{https://engineering.linkedin.com/distributed-systems/log-what-every-software-engineer-should-know-about-real-time-datas-unifying}{Blog here}
+\subsection{What is a log?}
+\begin{itemize}
+\item Record of ordering activities.
+\item Logs in databases: A database uses a log to write out information about the records they will be modifying, before applying the changes to all the various data structures it maintains.
+\item Logs in distributed systems:\textbf{State Machine Replication Principle:}
 
-%\includepdf[pages=-]{.pdf}
+If two identical, deterministic processes begin in the same state and get the same inputs in the same order, they will produce the same output and end in the same state.
+
+\end{itemize}
 \end{document}
+%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
+%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

### 2018-09-13 FS/presentation.tex
9.13

--- 2018-09-12 Templates/test/p.tex
@@
               
-\documentclass{beamer}
+\documentclass[xelatex]{beamer}
 %
@@
 \usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
+%\usepackage[utf8x]{inputenc}
+\usepackage{xeCJK}
+\usepackage{verbatim}
 
-\title[Your Short Title]{Your Presentation}
-\author{You}
-\institute{Where You're From}
-\date{Date of Presentation}
+\title[Your Short Title]{基于GlusterFS的数据分布策略研究}
+\author{陈辉}
+%\institute{Where You're From}
+\date{}
 
@@
 % Uncomment these lines for an automatically generated outline.
-%\begin{frame}{Outline}
-%  \tableofcontents
-%\end{frame}
+\begin{frame}{Outline}
+  \tableofcontents
+\end{frame}
+\section{Introduction}
+\begin{frame}{概述}
+本研究致力于在分布式（或高性能计算）环境下，针对不同工作负载进行冷热数据动态负载均衡。主要思想是：
+\begin{itemize}
+\item 对用户程序实时监控，抽取与IO操作相关性较大的行为特征;
+\item 根据用户IO读写历史对文件系统中的数据进行聚类;
+\item 将用户、用户程序特征与聚类后的数据进行关联;并根据访问时序对聚类后的数据进行粗略排序。
+\item 针对正在运行或即将运行的用户程序特征，将关联的数据（主要针对小文件）按时序加载至SSD.
+\end{itemize}
+\end{frame}
 
-\section{Introduction}
+\section{GlusterFS简介}
 
-\begin{frame}{Introduction}
+\begin{frame}{GlusterFS简介}
 
-\begin{itemize}
-  \item Your introduction goes here!
-  \item Use \texttt{itemize} to organize your main points.
-\end{itemize}
-
-\vskip 1cm
-
-\begin{block}{Examples}
+%\vskip 1cm
+\begin{block}{GlusterFS架构简述}
 Some examples of commonly used commands and features are included, to help you get started.
@@
 
+\begin{block}{GlusterFS tiering模块}
+\end{block}
 \end{frame}
 
-\section{Some \LaTeX{} Examples}
+\section{数据采集(监控)}
+\subsection{日志分析}
+\begin{frame}{日志分析}
+日志分析能够比较直接地比对分析用户程序运行与系统层IO活动的逻辑关联性.
+%此处应有图
 
-\subsection{Tables and Figures}
+\end{frame}
 
-\begin{frame}{Tables and Figures}
-
-\begin{itemize}
-\item Use \texttt{tabular} for basic tables --- see Table~\ref{tab:widgets}, for example.
-\item You can upload a figure (JPEG, PNG or PDF) using the files menu. 
-\item To include it in your document, use the \texttt{includegraphics} command (see the comment below in the source code).
-\end{itemize}
-
+\begin{comment}
 % Commands to include a figure:
@@
 \end{tabular}
-\caption{\label{tab:widgets}An example table.}
+\caption{An example table.}
 \end{table}
-
 \end{frame}
-
-\subsection{Mathematics}
-
-\begin{frame}{Readable Mathematics}
-
-Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
-$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
-      = \frac{1}{n}\sum_{i}^{n} X_i$$
-denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.
-
-\end{frame}
+\end{comment}
 

### 2018-09-25 CS/TLPI.tex
9.21
9.25

--- 2018-08-23 NDP/NDP.tex
@@
 }
-\newcommand{\page}[2]{\hyperlink{#1.pdf.#2}{link}}
+\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
+\newcommand{\book}[1]{\href[page=#1]{./books/TLPI.pdf}{(P#1)}}
 
-\title{Near-Data Processing}
+\title{The Linux Programming Interfaces}
+\author{陈辉}
 \date{}
 \begin{document}
-
 \maketitle
-
 \tableofcontents
 \newpage
-\part{文献}
+\section{History and Standards}
+\section{Fundamental Concepts}
+\subsection{The Kernel}
+\subsection{The Shell}
+\subsection{Users and Groups}
+\subsubsection*{Users}
+\begin{itemize}
+\item \textit{login name}
+\item \textit{user ID(UID)}
+\item \textit{Group ID}
+\item \textit{Home directory}
+\item \textit{Login shell}:the name of the program to be executed to interpret user commands.
+\end{itemize}
+These information of each user resides in \textit{password files}
+\subsubsection*{Groups}
+\subsubsection*{Superuser}
+userID = 0.
+\subsection{Single Directory Hierarchy, Directories, Links, and Files}
+Figure of single directory hierarchy.\book{71}
+\subsubsection*{FIle Types}
+\textit{The other file types}:\\
+devices, pipes, sockets, directories, and symbolic links.
+\subsubsection*{Directories and links}
+The links between directories establish the directory hierarchy.
+\subsubsection*{Symbolic links}
+\subsubsection*{Pathnames}
+\begin{itemize}
+\item \textit{absolute pathname}
+\item \textit{relative pathname}
+\end{itemize}
 
-%\includepdf[pages=-]{.pdf}
+\subsection{File I/O Model}
+\par\textit{universality of I/O}:The same system calls(\textit{open,read,write,close}) are used to perform I/O on \textbf{all types of files}.
+\subsubsection*{File descriptors}
+A nonnegative integer obtained by a call to \textit{open()}.\\
+Often 0 for input, 1 for output and 2 for errors or other abnormal messages.
+\subsection{Programs}
+\subsubsection*{Filters}
+\subsubsection*{Command-line arguments}
+
+\subsection{Processes}
+\subsubsection*{Process memory layout}
+\textit{segments}:
+\begin{itemize}
+\item \textit{Text}
+\item \textit{Data}
+\item \textit{Heap}
+\item \textit{Stack}
+\end{itemize}
+
+\subsubsection*{Process creation and execution}
+\textit{fork()}:\\
+The kernel creates the child process by making a duplicate of the parent process which inherits copies of parent's \textbf{data, stack, heap}.
+The text is placed in memory marked read-only shared by them.\\
+\textit{execve()}:\\
+child call execve() system calls to replace the origin segments with new target program.
+
+\subsubsection*{Process ID and parent process ID}
+\subsubsection*{Process termination and termination status}
+child call \textit{\_exit()} or be killed by a signal.\\
+parent \textit{wait()} for child's \textit{termination status}.
+\subsubsection*{Process user and group identifiers}
+\begin{itemize}
+\item \textit{Real user ID and real group ID}
+\item \textit{Effective user ID and effective group ID}
+\item \textit{Supplementary group IDs}
+\end{itemize}
+
+\subsubsection*{The \textit{init} process}
+The \textit{init} is the parent of all processes with a constant PID = 1.\\
+
+\subsubsection*{Daemon processes}
+background
+\subsubsection*{Environment list}
+
+\subsection{Memory Mappings}
+\textit{mmap()}:
+
+\subsection{Static and Shared Libraries}
+\subsubsection*{Static libraries}
+A static library is essentially a structured bundle of compiled object modules. To use functions from it we specify that library in the \textbf{link} command used to \textbf{build} a program.
+\subsubsection*{Shared libraries}
+Shared libraries were designed to address the wasting problems with static libraries.
+\begin{itemize}
+\item While building: the linker writes a record into the executable.
+\item While runtime: \textit{dynamic linker} ensures the required shared libraries are found and loaded to the memory.
+\end{itemize}
+
+\subsection{Interprocess Communication(IPC) and Synchronization}
+The set of mechanisms for interprocess communication(IPC):
+\begin{itemize}
+\item \textit{signals}
+\item \textit{pipes}
+\item \textit{sockets}
+\item \textit{file locking}
+\item \textit{message queues}
+\item \textit{semaphores}
+\item \textit{shared memory}
+\end{itemize}
+
+\subsection{Signals}
+Signals are often described as ``software interrupts''
+\subsection{Threads}
+
 \end{document}
+
+%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
+%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

### 2018-09-26 CS/TLPI.tex
9.26

@@
 \subsection{Threads}
+Threads \textbf{share}
+\begin{itemize}
+\item Text(for program codes).
+\item Data.
+\item Heap.
+\item virtual memory.
+\item global variables.(for communication)
+\end{itemize}
+Threads \textbf{differ in}
+\begin{itemize}
+\item Stack.
+\item local variables.
+\item function call linkage information(why?).
+\end{itemize}
+Threads' \textbf{advantages}
+\begin{itemize}
+\item easy to share data rather than multiprocesses.
+\item good for parallel processing
+\end{itemize}
+
+\subsection{Process Groups and Shell Job Control}
+\subsection{Sessions, Controlling Terminals, and Controlling Processes}
+\subsection{Pseudoterminals}
+A pseudoterminal is a \textbf{pair of connected virtual devices} known as \textbf{master and slave}.\\
+Master drives the user program and slave drives terminal-oriented program. This connection is like a bridge. e.g. \textit{telnet and ssh}.
+\subsection{Date and Time}
+\begin{itemize}
+\item \textit{Realtime}.
+\item \textit{Process time}.
+\end{itemize}
+
+\subsection{Client-Server Architecture}
+\subsection{Realtime}
+\href{https://www.cl.cam.ac.uk/~mgk25/linux-posix.1b.txt}{POSIX.1b}:
+\subsection{The /proc File System}
+A virtual file system that provide an \textbf{interface to kernel data structures}.
+
+\section{System Programming Concepts}
+
+\subsection{System Calls}
+\book{87}
+\subsection{Library Functions}
+\subsection{The standard C Library; The GNU C Library(glibc)}
+\subsection{Handling Errors from System Calls and Library Functions}
+
+\subsection{Notes on the Example Programs in this book}
+
+\subsubsection{Command-Line Options and Arguments}
+\subsubsection{Common Functions and Header Files}
+\book{95}
+
+\subsection{Portability Issues}
 

### 2018-10-17 CS/TLPI.tex
9.27

@@
 
+\section{File I/O}
+Keypoints:
+\begin{itemize}
+\item System call APIs to perform file I/O.
+\item File descriptor.
+\end{itemize}
+
+\subsection{Overview}
+Key word:\textit{file descriptor}
+
+\setcounter{section}{40}
+\section{Fundamentals of Shared Libraries}
+
+\subsection{Object Libraries}
+\book{833}
+\textbf{Object Library}: A set of object files.\\
+\subsection{Static Libraries(archives)}
+\subsubsection*{Creating and maintaining a static library}
+Syntax:
+\begin{lstlisting}
+\$ ar \textit{options archive object-files}
+\end{lstlisting}
+\textbf{Conventional form of static libraries}: lib\textit{name}.a.
+\begin{lstlisting}
+	\$ gcc -g -c mod1.c mod2.c
+	\$ ar r libdemo.a mod1.o mod2.o
+	\$ rm mod1.o mod2.o
+\end{lstlisting}
+Delete modules from the archive:
+\begin{lstlisting}
+	\$ ar d libdemo.a mod2.o
+\end{lstlisting}
+
+\subsubsection*{Using a static library}
+Basic way:
+\begin{lstlisting}
+\$ gcc -g -c prog.c
+\$ gcc -g -o prog prog.o libdemo.a
+\end{lstlisting}
+Alternative way:
+\begin{lstlisting}
+\$ gcc -g -o prog prog.o -ldemo
+\end{lstlisting}
+'-ldemo' means '-l' and archive without lib prefix and .a suffix which resides in one of the standard directories(e.g. /usr/lib)
+
+\subsection{Overview of Shared Libraries}
+\subsection{Creating and Using Shared Libraries}
+\textbf{ELF(Executable and Linking Format shared libraries)}:ELF is the format employed for executables and shared libraries on modern linux.
+\subsubsection{Creating a Shared Library}
+\begin{lstlisting}
+\$ gcc -g -c -fPIC -Wall mod1.c mod2.c mod3.c
+\$ gcc -g -o -shared -o libfoo.so mod1.o mod2.o mod3.o
+\end{lstlisting}
+\textbf{Remark.} Unlike static libraries, object modules cannot be add or deleted from previously built shared library(why?)\\
+\subsubsection{Position-Independent Code}
+\textit{-fPIC} specifies that the compiler generate position-independent code.
+How to check whether an object file has been compiled with \textit{-fPIC}\book{882}
+
+\subsubsection{Using a Shared Library}
+Two main steps to utilize shared library:
+\begin{itemize}
+\item Embedding the name of the shared library inside the executable during linking.
+\item Resolving the embedding library name: performed by \textit{dynamic linker}, named \textbf{/lib/ld-linux.so.2}.
+\end{itemize}
+\textbf{The LD\_LIBRARY\_PATH} enveironment variable. \book{840}
+
+\subsubsection{The Shared Library Soname}
+
 \end{document}

### 2018-11-06 FS/overview.tex
nothing
11.05

--- 2018-07-29 FS/overview.tex
@@
 \documentclass{article}
+\usepackage{amsmath}
+\usepackage{pdfpages}
+\usepackage{verbatim}
 \usepackage{xeCJK}
 \usepackage{hyperref}
-\title{Overview}
+\usepackage{listings}
+\lstset{
+ columns=fixed,       
+ numbers=left,                                        % 在左侧显示行号
+ numberstyle=\tiny\color{gray},                       % 设定行号格式
+ frame=single,                                          % 不显示背景边框
+ keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
+ numberstyle=\footnotesize\color{darkgray},           
+ commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
+ stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
+ showstringspaces=false,                              % 不显示字符串中的空格
+ language=c++,                                        % 设置语言
+}
+\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
+\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}
+
+\title{Near-Data Processing}
+\author{陈辉}
 \date{}
 \begin{document}
-
 \maketitle
-
 \tableofcontents
 \newpage
-\part{环境配置}
-\section{虚拟机}
-\begin{itemize}
-\item \href{https://www.howtogeek.com/117635/how-to-install-kvm-and-create-virtual-machines-on-ubuntu/}{Installing qemu-kvm}
+\section{Distributed-Storage-Algorithm-for-Geospatial-Image-Data-Based-on-Data-Access-Patterns}
 
-\end{itemize}
-\section{GlusterFS}
+\includepdf[link=true,pages=-,fitpaper]{./papers/Distributed-Storage-Algorithm-for-Geospatial-Image-Data-Based-on-Data-Access-Patterns.pdf}
 
 \end{document}
+%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
+%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

### 2019-09-10 CS/note_TLPI.tex
paper

--- 2018-10-17 CS/TLPI.tex
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{dsfont}
+\usepackage{unicode-math}
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
+\usepackage{graphicx}
+\graphicspath{{./images/}}
+
 \usepackage{pdfpages}
@@
 \usepackage{hyperref}
+%\usepackage{apacite}
+\usepackage{natbib}
+\usepackage{grffile}
 \usepackage{listings}
@@
  stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
- showstringspaces=false,                              % 不显示字符串中的空格
+ showstringspaces=true,                              % 显示字符串中的空格
  language=c++,                                        % 设置语言
 }
-\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
-\newcommand{\book}[1]{\href[page=#1]{./books/TLPI.pdf}{(P#1)}}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,
+    urlcolor=cyan,
+}
+%--------Commands for local pdf reference------%
+\newcommand{\citeint}[2]{\cite{#1}\hyperlink{./references/#1.pdf.#2}{(P#2)}}
+\newcommand{\citeext}[2]{\href[page=#2]{../references/#1.pdf}{(P#2)}}
+\newcommand{\citeinclude}[1]{\includepdf[link=true,pages=-,fitpaper=true]{./references/#1.pdf}}
+\newcommand{\book}[1]{\citeext{TLPI}{#1}}
+%--------Commands/Operators for math------%
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
+%--------Environments for math------------%
+\newcounter{topic}[subsection]
+\newenvironment{defi}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Definition~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
+\newenvironment{theo}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Theorem~\thesubsection.\thetopic~} \rmfamily }{\medskip}
+\newenvironment{coro}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Corollary~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
+\newenvironment{lemm}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Lemma~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
+\newenvironment{exam}[1]{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Example~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
+
+\newenvironment{rema}[1]{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
+   \noindent \textbf{Remark~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
+\newenvironment{prof}{\par\medskip \noindent \textit{Proof.}~\rmfamily}{\medskip}
 
@@
 \subsubsection{The Shared Library Soname}
+\book{884}
+
+\setcounter{section}{5}
+\section{Processes}
+\subsection{Processes and Programs}
+\href{https://en.wikipedia.org/wiki/Executable\_and\_Linkable\_Format}{Executable and Linking Format}
+\subsection{Process ID and Parent Process ID}
+\subsection{Memory Layout of a Process}
+\textit{segments}:\\
+The memory allocated to each process. Including:
+\begin{itemize}
+        \item \textit{text segment}: Machine-language instructions. Read-only, shared. \\
+        \item \textit{Initialized data segment}: global and static variables explicitly initialized. \\
+        \item \textit{Uninitialized data segment}. \\
+        \item \textit{Stack}. One stack frame for each current called function. \\
+        \item \textit{Heap}: dynamically allocated data.
+\end{itemize}
+\subsection{Virtual Memory Management}
+Figure: Typical memory layout of a process.\book{163}\\
+\textcolor{green}{\textit{pages}}:\\
+A virtual memory scheme splits the memory used by each program into small fixed-size units called pages. \\
+\textit{page table}: \book{164} \\
+Processes can use \textit{shmget()} and \textit{mmap()} to explicitly request sharing of memory regions with other processes, for the purpose of \textcolor{red}{interprocess communication}. \\
+
+\subsection{The Stack and Stack Frames}
+\href{http://www.cs.uwm.edu/classes/cs315/Bacon/Lecture/HTML/ch10s07.html}{See this lecture} \\
 

### 2019-09-10 FS/pr_stacker.tex
paper

\documentclass{beamer}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{unicode-math}
\usepackage{verbatim}
\usepackage{xeCJK}
\mode<presentation> {
\setbeamertemplate{footline}[frame number]
\beamertemplatenavigationsymbolsempty
% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Stacker]{\textit{Stacker: An Autonomic Data Movement Engine for Extreme-Scale Data Staging-Based In-Situ Workﬂows}} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{} % Your name
\institute[] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
%University of California \\ % Your institution for the title page
\medskip
%\textit{john@smith.com} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}
\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Outline} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Background and Motivation} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

%\subsection{Data Staging and In-situ Workflows} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{In-situ End-to-end Workflows}
\begin{block}{End-to-end Workflows}
End-to-end scientiﬁc workﬂows include coupled simulations along with data handling/processing services such as analysis and visualization. Running at extrem-scales, the excution of these simulations on leadership class systems present significant data management challenges due to the increasing volume of data.
\end{block}
\begin{block}{Data Staging}
Many of current approaches use data staging, leveraging memory at staging nodes to hold data as it moves between the components of the workﬂow.
\end{block}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Typical Data Staging Frame}
\begin{figure}
        \includegraphics[width=\textwidth]{images/stacker_fig_1.jpg}
        \caption{A typical data staging framework with in-memory data staging. Each of the data staging nodes/servers is equipped with SSDs.}
\end{figure}
\end{frame} 
%------------------------------------------------

%------------------------------------------------
\begin{frame}
\frametitle{Bottlenecks and Challenges}
\begin{block}{Capacity restrictions for DRAM}
The extreme-scale data can easily exceed DRAM's capacity. Large amount of data must be offloaded/load between memory and burst buffers.
\end{block}

\begin{block}{Latency and throughput gap}
Burst buffers have much longer access latencies and lower throughput compared to main memory. Thus intelligent data prefetching based on access patterns can hide this disk access and data transfer latency.
\end{block}
%\begin{itemize}
%        \item The extreme-scale data can easily exceed DRAM's capacity. Large amount of data must be offloaded/load between memory and burst buffers.\\
%        \item Burst buffers have much longer access latencies and lower throughput compared to main memory. Thus intelligent data prefetching based on access patterns can hide this disk access and data transfer latency. \\
%        \item A component of the workflow which access offloaded data in burst buffer would benefit from efficient \textbf{prefetching} approches.
%        \item Current prefetching approches and their flaws:
%                \begin{enumerate}
%                        \item Methods based on user-defined hints. They work well for simple applications but struggle in complex tasks due to the manual tuning. \\
%                        \item Methods based on spatial/temporal locality. They work well with contiguous or fixed strided access patterns in a single application, whereas not effective for variable strided access nor in multi-application workflow.
%                \end{enumerate}
%\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Related Works For Data Prefetching}
\begin{block}{Methods based on user-defined hints}
    They work well for simple applications but struggle in complex tasks due to the manual tuning. \\
\end{block}
\begin{block}{Methods based on spatial/temporal locality} 
    They work well with contiguous or fixed strided access patterns in a single application, whereas not effective for variable strided access nor in multi-application workflow.
\end{block}
\begin{block}{Methods based on N\textit{th}-order Markov chain}
    These works mainly risides in kernel space and do prefetching at the granularity of pages.        
\end{block}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Contributions of \textit{Stacker}}
    \begin{itemize}
        \item \textit{Stacker} implements N-gram model for abstracting access patterns and predicting requests automatically.
        \item Rather than modeling individual applications and their access patterns, \textit{stacker} models the data accesses among mutiple components of application workflows.
    \end{itemize}

%The goal of this paper is to explore machine learning based approaches to capture the data access patterns between components of staging-based in-situ application workﬂows, and to use these learned access patterns to move data between the storage layers of the staging service in an autonomous manner.

\end{frame}
%------------------------------------------------
\section{Introduction to Stacker}
%\subsection{Main Architecture}
\begin{frame}
%\subsection{Overview}
\frametitle{Main Architecture}
\begin{figure}
        \includegraphics[width=\linewidth]{images/stacker_fig_2.png}
        \caption{Architecture of multi-tiered staging framework of Stacker}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\textit{Dataspaces}}
%\begin{block}{\textit{Dataspaces}}
%\textit{Data-Spaces} is the fundamental framework of data-staging services, which offers a virtual shared-space abstraction between DRAM and on-node SSDs.
%consists of query engine layer, data indexing layer and data storage layer.
%Data-Spaces is a ﬂexible interaction and coordination substrate for end-to-end scientiﬁc workflows.
%\end{block}
\begin{figure}
\includegraphics[width=\textwidth]{images/dataspaces.png}
\caption{\textit{Data-Spaces} is the fundamental framework of data-staging services, which offers a virtual shared-space abstraction between DRAM and on-node SSDs.}
\end{figure}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Shared-space between DRAM and SSDs}
%            \begin{block}{Data Object/Block Storage Layer}
Within \textit{Data-Spaces}, a name conversion utility between in-meomory objects and in-storage files is implemented. By this means, data loading requests are analyzed and predicted in object/variable level rather than files. Metadata for files in data-staging servers are formed as below:
%            \end{block}
            \begin{tabular}{|c|c|}
                    \hline
                    \textbf{Metadata} & \textbf{Description} \\
                    \hline
                    DSG\_ID & ID of the server storing the object.\\
                    \hline
                    var\_name & name of the variable in workflow.\\
                    \hline
                    lb & Starting offset of the object in the global bounding box.\\
                    \hline
                    ub & Ending offset of the object.\\
                    \hline
                    ver & Version number of the object.\\
                    \hline
            \end{tabular}
%\par A bounding box is a geometric descriptor specifying the range of data along each dimension of the application domain. All of this information is concatenated into a string to create an unique ﬁle-name for each object. This object is then written as a ﬁle to the SSD using POSIX write APIs. When an object stored in SSD is requested, the ﬁle-name is functionally computed and appropriate data from that speciﬁc ﬁle is sent to the requesting client. 
\end{frame}
%------------------------------------------------
%\subsection{Data Placement Module}
\begin{frame}
%\subsubsection{Data Placement Module}
\frametitle{Data Placement Module}

%    \begin{block}{Data Placement Module}
%            This module records data access history(metadata) and implements efficient prefetching alogorithm to enhance the reading performance.
In this module, access history is stored in a hash-table for succeeding prediction. As an example, consider the case in which several applications are requesting data from variables: \textit{$\alpha \rightarrow \beta \rightarrow \gamma \rightarrow \delta$}, successively. 
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Step 1: Data Access History Recording/Analyzing}
Supppose we implement 4-gram model at most in this example. According to the requests $\alpha \rightarrow \beta \rightarrow \gamma \rightarrow \delta$, the 4-gram, 3-gram and 2-gram gram-frequency pairs in the hash-table are updated as below:
    \begin{center}
    \begin{table}
    \begin{tabular}{|c|c|}
            \textbf{Grams} & \textbf{Occurrence frequency} \\
            $\alpha, \beta, \gamma, \delta$ & +1 \\
            $\alpha, \beta, \gamma$ & +1 \\
            $\beta, \gamma, \delta$ & +1 \\
            $\alpha, \beta$ & +1 \\
            $\beta, \gamma$ & +1 \\
            $\gamma, \delta$ & +1 \\
            ... & ... \\
    \end{tabular}
    \caption{An hash-table for variable access history.}
    \end{table}
    \end{center}
%    \end{block}

\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Step 2: Predicting}
            This algorithm is a \textit{hierarchical prediction} that would search for the previous grams as long as possible in the hash-table.
    \begin{center}
            \includegraphics[width=.5\textwidth]{images/stacker_fig_3.png}
    \end{center}
%\end{column}
%\end{columns}
\end{frame}

%------------------------------------------------
\begin{frame}
%\begin{columns}
%\begin{column}{.5\textwidth}
\frametitle{Step 3: Prefetching and Evicting}
            A FIFO queue is maintained for the prefetch partition. The staging server runs two extra thread, one for prefetching predicted data from Step 2, and another for evicting the oldest data in cache.
\end{frame}

\section{Evaluation}
\begin{frame}
\frametitle{Evaluation}
To evaluate Stacker, both synthetic experiments and real scientific workflow were tested.
\begin{block}{Environment for Synthetic Experiment}
        The Caliburn Supercomputer at the Rutgers Discovery Informatics Institude, which consists of 560 nodes, each containing Dual Intel Xeon E5-2695v4, 18-Core processors with 256 GB of RAM and a 400GB Intel NVMe drive per node.
\end{block}
\begin{block}{Environment for Real Scientific Workflow}
Titan Cray XK7 system. It has 18,688 compute nodes and each node is equipped with 16-core AMD 6200 series Opteron processor and 32 GB memory. \\

They used the combustion DNS-LES simulation/analysis from the S3D comustion and analysis workflow.
\end{block}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Synthetic Experiments}
\begin{center}
        \includegraphics*[width=\textwidth]{images/stacker_fig_4.png}
\end{center}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Real Scientific Workflows}
\begin{center}
        \includegraphics*[width=\textwidth]{images/stacker_fig_5.png}
\end{center}
\end{frame}
%------------------------------------------------

%------------------------------------------------

%------------------------------------------------

%\begin{frame}[fragile] % Need to use the fragile option when verbatim is used in the slide
%\frametitle{Citation}
%An example of the \verb|\cite| command to cite within the presentation:\\~

%This statement requires citation \cite{p1}.
%\end{frame}

%------------------------------------------------

%\begin{frame}
%\frametitle{References}
%\footnotesize{
%\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
%\bibitem[Smith, 2012]{p1} John Smith (2012)
%\newblock Title of the publication
%\newblock \emph{Journal Name} 12(3), 45 -- 678.
%\end{thebibliography}
%}
%\end{frame}

%------------------------------------------------

%\begin{frame}
%\Huge{\centerline{The End}}
%\end{frame}

%----------------------------------------------------------------------------------------

\end{document}

### 2019-09-10 master/paper.tex
paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Path2Vec: An NLP Based Mechanism for File Access Pattern Detection\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
    Many scientific applications spend a large proportion of the execution time to access files. 
    To narrow the increasing gap between computing and I/O performance, several optimization techniques were adopted, 
    such as data prefetching and data layout optimization. However, the effectiveness of these optimization processes heavily 
    depends on the understanding of the I/O behavior. Traditionally, spatial locality and temporal locality
    are mainly considered for data prefetching and scheduling policy. Whereas for some complex workloads, the file access pattern 
    is hard to reveal due to ... 
    We propose Path2Vec, an embedding approach to transform filenames to vectors, thus allowing further analysis of access patterns. 
    To evaluate the effectiveness of this mechanism, we implemented a

\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

\section{Introduction}
Distributed file systems such as HDFS\cite{HDFS}, GlusterFS[], Ceph\cite{Ceph}, Lustre[] \textcolor{red}{etc}. have been widely deployed as back-end storage systems for parallel/distributed applications.
with the data scale continuously increased, i/o access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
Caches(burst buffers?) with non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.

\textcolor{red}{Traditional methodoligies: mainly apllying spatial and temporal locality}
For purpose of caching data from lower storage in predictable manner, access pattern detection is essential.
Traditionally, spatial locality and temporal locality are most generally considered facts. 
\textit{Readahead} is a basic mechanism implemented by most file systems\cite{WhyDoes} including linux kernel, which prefeches constant size of data from a opened file to the cache. 
For workloads excuting sequential read, this approach benefits a lot due to the simple and definite pattern.
Unfortunately, many applications especially sientific ones usually do not follow sequential behavior(\textcolor{yellow}{IO acceleration with patter detection}). 
\textcolor{red}{How about small files workloads?}

\textcolor{red}{Curently works}

\textcolor{red}{Briefly introducing your work to address the drawbacks mentioned above.}

The main contributions of this paper can be summerized as follow.
\begin{itemize}
    \item We design and implement a filename embedding model named path2vec, 
    which traverses the user's whole directory and captures naming conventions and semantic relations among directories and files.
    \item A tracing translator is inserted into GlusterFS's storage stack, which is able to collect file access histories and represent these histories as vectors.

\end{itemize}

\section{Related Work}
N-gram staging: high level works on data libraries
C-miner: low level on block-rate optimization.
meta data access optimizations.

\section{Background and Motivation}
\subsection{Introduction to GlusterFS}
GlusterFS is a scalable distributed filesystem which is suitable for data-intensive workloads such as cloud storage and high performance computing.
It aggregates various storage servers over Ethernet or Infiniband RDMA interconnect into one large parallel network file system.
Servers are typically deployed as storage bricks.

Since version 3.7, the newly implemented feature \textit{tiring} enables different sotrage types to be used by the same logical volume.
As fig shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
With fine-tuned prefeching and cache replacing policy, large propotion of I/O requests are forwarded to \textit{hot} bricks, thus significantly decreasing access latency.
In this case, we can reframe(\textcolor{red}{EDIT}) caching/prefeching optimization tasks to binary classification problems,
where the objective is to dynamically decide whether a file is \textit{hot} or \textit{cold}.

\subsection{Word Embedding}
The concept word embedding is a set of language models for distributed representations of words in \textit{Natural Language Processing}(NLP), 
aiming at mapping natural words to real number vectors based on context provided by specific corpora.
These mapping mechanisms include neural networks, dimensionality reduction on the word co-occurrence matrix, probabilistic methods etc. \textcolor{blue}{refs}

The most widely utilized model is \textit{skip-gram algorithm}\cite{SkipGram}, 
which trains a neural network to predict whether a word is likely to show up near another.
Given a word vocabulary of size $W$, where a word is identified by $w \in {1,\dots,W}$, 
and a corpus consists of a sequence of words $w_1, \dots, w_T$, the objective of skip-gram algorithm is to maximize the following log probability:
\begin{equation}
\frac{1}{T}\sum_{t=1}^{T}\sum_{-c \leq j \leq c,j \neq 0} \log p(w_{t+j} | w_t),
\end{equation}
Where $w_t$ denotes the target word at position $t$ in the training corpus and $c$ is the size of context window.
A basic definition of $p(w_t+j | w_t)$ is the softmax function:
\begin{equation}
%    p(w_O | w_I) = \frac{\exp{v'_{w_O}^{\top}}{b}
\end{equation}
However, it's generally impractical to calculate softmax function due to the tremendous \textbf{(EDIT)}computational complexity,
as the size of vocabulary may be too large.
To estimate ...

\subsection{Gated Recurrent Neural Networks}
RNNs(\textit{Recurrent Neural Networks}) have been widely utilized and shown exellent performance in multiple NLP tasks,
such as speech recognition, machine translation and text emotion classification etc.
The RNN is an extension of a conventional feedforward neural network, which is able to process a variable-length sequence input.
Given a sequence input $x = (x_1, x_2, \dots, x_T)$, the RNN updates its recurrent hidden state $h_t$ by
\begin{equation}
    \mathbf{h_t}=
        \begin{cases}
            0, &t=0 \\
            \phi(\mathbf{h_{t-1}, \mathbf{x_t}}), &\text{otherwise}
        \end{cases}
\end{equation}
Where $\phi$ is a nonlinear function calculating current hidden state $h_t$ based on last state $h_{t-1}$ and current input $x_t$.

Gated recurrent unit(GRU)\textcolor{blue}{ref} is a gating mechanism in RNNs, 
which is like a long short-term memory(LSTM)\textcolor{blue}{ref} with forget gate but has fewer parameters.
See \textcolor{blue}{fig}

\section{Design}
\subsection{Path Embedding Model}
Since words embedding mechanisms have significantly promoted the performance of plenty of NLP tasks, 
we assume that these methodologies are suitable in analytics and optimizations for posix file systems as well.
\textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim(\textcolor{red}{EDIT}) that \textit{a} and \textit{b},
\textit{b} and \textit{c} are parent-child pairs, while \textit{c} and \textit{d} are a pair of brothers with the same parent \textit{b}.
Or, intuitively, they are logically close to each other in this directory tree. 
This basic relation is analogous to 2-Grams (\textcolor{red}{EDIT}) in natural language models.

Formally, given a directory tree accessed by a specific workload such as compiling, 
it is assumed that the naming conventions and directory structure are regularly formed by producers or users.
Thus it is possible to form a vocabulary and train an embedding model to represent each directory/file name as a vector.

To generate corpora for training purpose,
we recursively traverse the target directory from root entry and print the paths into a txt file line by line.
After that, the Skip-gram algorithm is invoked to train a embedding model, 
which finally provides a vocabulary for all the occured directory/file names and a table consists of vectors for these names.

\subsection{Access Pattern Analytics with Gated Recurrent Neural Network}
\subsubsection{Data pre-processing}
To collect file access histories, we insert a trace translator into GlusterFS.
So far, we mainly focus on file \textit{open} operation in order to detect when, how and what files does the workload start to access during its lifetime,
attemtpting to reveal its underlying access patterns beyond basic locality. 
As \textbf{fig} illustrated, the components of parameter \textit{path} in each \textit{open} request are transformed to vectors and summed up.\textcolor{red}{edit}

\textcolor{blue}{A figure here}

Finally, a sequence of vectors $\mathbf{x}=(\mathbf{x_1}, \dots, \mathbf{x_T})$ representing access history of size $T$ have been generated.

\subsubsection{GRU-based model building\textcolor{red}{edit}}
In our design, we utilize a single-layer GRU to calculate and update the hidden state, which implicitly represents the access pattern of the target workloads. 
Given dataset $\mathbf{x} = (\mathbf{x}_1,\dots,\mathbf{x}_T)$ representing a sequence of file access history excuted by the target workload, 
we take these vectors as input sequence for the GRU and train the model.

At time $t$, the activation $h_t^{(j)}$, which denotes the $j$th element of the hidden state $\mathbf{h}_t$, is a linear interpolation between the previous activation $h_{t-1}^{(j)}$ and the candidate activation $\tilde{h}_t^{(j)}$:
\begin{equation}
    h_t^{(j)} = (1-z_t^{(j)}) h_{t-1}^{(j)} + z_t^{(j)}\tilde{h}_t^{(j)},
\end{equation}
Where $z_t$ is denoted as an \textit{update gate}, calculated by a sigmoid function over input $\mathbf{x_t}$ and previous state $\mathbf{h_{t-1}}$:
\begin{equation}
z_t^{(j)} = \sigma(W_z \mathbf{x}_t + U_z \mathbf{h}_{t-1})^{(j)}
\end{equation}
The candidate acitivation $\tilde{h}_t^{(j)}$ is computed by:
\begin{equation}
    \tilde{h}_t^{(j)} = \tanh(W \mathbf{x}_t + U (\mathbf{r}_t \odot \mathbf{h}_{t-1}))^{(j)}
\end{equation}
Where $\mathbf{r}_t$ are \textit{reset gates} and $\odot$ is a pointwise multiplication(Hadarmard product).
The reset gate is calculated by
\begin{equation}
    r_t^{(j)} = \sigma(W_r \mathbf{x}_t + \mathbf{U}_r \mathbf{h}_{t-1})^{(j)}
\end{equation}
For purpose of discriminating files between \textit{hot} and \textit{cold}, 
our goal is to train the GRU to provide appropriate hidden states for classification. 
We denote $N$ as the approximation of the number of files fit in the cache,
thus at time $t$, the following $N$ files(vectors) are labeled as \textit{hot}, i.e., positive samples, 
while the others are labeled as \textit{cold}(negative).
As long as $\mathbf{h}_t$ is calculated, the objective is to maximize the log probability
\begin{equation}
    \label{eq.obj}
    \sum_{i=1}^N \log P(\mathbf{x}_{t+j}|\mathbf{h}_t)
\end{equation}
Where we calculate the probability $P(\mathbf{x}_{t+j}|\mathbf{h}_t)$ by
\begin{equation}
    P(\mathbf{x}_{t+j}|\mathbf{h}_t) = \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Thus we obtain the loss function for training
\begin{equation}
    arg\,max L(\theta) = \sum_{i=1}^N \log \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Where the parameter $\theta = \{W_z, U_z, W, U, W_r, U_r\}$.
We train this GRU with BPTT(backpropagation through time)\textcolor{red}{ref}.

\section{Evaluation}
\subsection{Experiment and Parameter Settings}
We choose compiling workloads for experiments and collect a few different repositories from Github,
including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
We split these repositories into two groups, 10 arbitrary repositories for training and the others for testing.

To evaluate the performance of our model,

\subsection{Results}

%\subsection{\textcolor{red}{EDIT}Similarity Experiment for Directory/File Names}
%In this part, we picked up \textcolor{red}{edit} most frequently occured names from vocabulary, which is generated from the training group of repositories with Skip-gram algorithm.
%We utilize PCA(\textit{Principal Component Analysis}) to project these \textcolor{red}{edit} vectors(\textcolor{red}{EDIT}) into a 2-D graph.
%As fig(\textbf{refhere}) illustrates,

%\subsection{\textcolor{red}{edit}{Evaluation for dynamically file classification}}
\section{Conclusion}
In this paper, we systematically discuss the similarity between natural language processing and posix file systems,
and propose a new approch to represent posix file/direcory names with Skip-gram algorithm. 
With this embedding mechanism, we map the file/directory names into a high dimension vector space, 
where the relation between files can be dipicted by dot production of these two vectors.

Based on this embedding mechanism, we exploit a single-layer GRNN(Gated Recurrent Neural Network) taking file access history as sequence input.
With well trained GRU, we are able to encode the access pattern to the hidden state and dynamically decide whether a file is \textit{hot} or \textit{cold},
thus providing hints for caching/prefeching and cache replacing policies.

There are several works to accomplish in the future. First, the model should be deployed in tiering translator in GlusterFS,
thus making it possible to exploit our model in real fils system for optimization purpose. 
Also, our work should be scaled to more real world workloads rather than compiling.
\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2019-09-10 master/paper.tex
paper

@@
 have been widely deployed as back-end storage systems for parallel/distributed applications.
-with the data scale continuously increased, i/o access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
+with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
 In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
@@
 \section{Related Work}
-N-gram staging: high level works on data libraries
-C-miner: low level on block-rate optimization.
-meta data access optimizations.
+The I/O subsystem is becoming the bottleneck of high performance distributed systems, 
+especially there are many communication intensive applications in them \cite{Related_Network_I/O_load_based}.
+In order to achieve potential performance enhancements of storage systems, 
+a variety of I/O history analysis-based I/O optimization mechanisms have been proposed previously 
+\cite{Related_Multi_Layer_Event_Trace_Analysis} \cite{Related_Towards_an_I/O_tracing_framework_taxonomy} \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related} \cite{Scalable_IO_Tracing_Related}.
+However, existing approaches including aforementioned ones have mostly focused on classifying I/O access patterns by analyzing either the history of applications’ I/O requests
+\cite{Parallel_IO_Prefetching_Related} \cite{Learning_To_Classify_Related}
+or the track of block access events \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related}, 
+so that the analyzed results can be used for directing I/O optimization strategies, such as data prefetching.
+The mechanism of data prefetching focuses on how to forecast future possible read requests, and thus, 
+the accuracy of request prediction is critical to the effectiveness and applicability of data prefetching.
+
+There is a wide range of sophisticated approaches to fulﬁll data prefetching, 
+which utilize hidden Markov models, 
+neural networks or other predictive algorithms to forecast I/O operations by analyzing I/O access patterns of the application 
+\cite{Parallel_IO_Prefetching_Related} \cite{IO_Acceleration_with_Related} \cite{An_Automatic_Prefetching_Related} \cite{Reducing_File_System_Latency_Related} \cite{Automatic_ARIMA_Related}.
+In summary, these mechanisms employ specific hard-coded algorithms to predict the application's future I/O access requests based on past I/O tracks for prefetching data.
 
@@
 In this paper, we systematically discuss the similarity between natural language processing and posix file systems,
-and propose a new approch to represent posix file/direcory names with Skip-gram algorithm. 
+and propose a new approach to represent posix file/direcory names with Skip-gram algorithm. 
 With this embedding mechanism, we map the file/directory names into a high dimension vector space, 

### 2019-09-10 master/paper.tex
paper

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{url}
 \usepackage{cite}
@@
 \section{Introduction}
-Distributed file systems such as HDFS\cite{HDFS}, GlusterFS[], Ceph\cite{Ceph}, Lustre[] \textcolor{red}{etc}.
-have been widely deployed as back-end storage systems for parallel/distributed applications.
+Distributed file systems such as HDFS\cite{HDFS}, GlusterFS\cite{GlusterFS}, Ceph\cite{Ceph}, Lustre\cite{Lustre}, etc., have been widely deployed as back-end storage systems for parallel/distributed applications.
 with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
 In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
-Caches(burst buffers?) with non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.
+Caches with high throughput and low latency devices like non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.
 
-\textcolor{red}{Traditional methodoligies: mainly apllying spatial and temporal locality}
 For purpose of caching data from lower storage in predictable manner, access pattern detection is essential.
@@
 For workloads excuting sequential read, this approach benefits a lot due to the simple and definite pattern.
-Unfortunately, many applications especially sientific ones usually do not follow sequential behavior(\textcolor{yellow}{IO acceleration with patter detection}). 
-\textcolor{red}{How about small files workloads?}
-
-\textcolor{red}{Curently works}
-
-\textcolor{red}{Briefly introducing your work to address the drawbacks mentioned above.}
+Unfortunately, many applications especially sientific ones usually do not access files sequentially.
 
@@
 \begin{itemize}
-    \item We design and implement a filename embedding model named path2vec, 
-    which traverses the user's whole directory and captures naming conventions and semantic relations among directories and files.
-    \item A tracing translator is inserted into GlusterFS's storage stack, which is able to collect file access histories and represent these histories as vectors.
+    \item We propose an approach to embedd the names of files or directories with Skipgram algorithm, 
+    mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
+    \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
+    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to catch I/O access pattern and encode it with hidden states of the GRU.
+    We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.
 

### 2019-09-10 master/paper.tex
paper

@@
 
-\title{Path2Vec: An NLP Based Mechanism for File Access Pattern Detection\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{An RNN Based Mechanism for File Prefeching\\
+%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+%should not be used}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Hui Chen}
+\IEEEauthorblockA{\textit{National University of Defense Technology} \\
+Changsha, China\\
+code2hack4ever@gmail.com}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{2\textsuperscript{th} Enqiang Zhou*}
+\IEEEauthorblockA{\textit{National University of Defense Technology} \\
+%\textit{name of organization (of Aff.)}\\
+Changsha, China\\
+eqzhou@nudt.edu.cn}
 }
@@
 \begin{abstract}
-    Many scientific applications spend a large proportion of the execution time to access files. 
+    Many applications spend a large proportion of the execution time to access files.
     To narrow the increasing gap between computing and I/O performance, several optimization techniques were adopted, 
@@
     depends on the understanding of the I/O behavior. Traditionally, spatial locality and temporal locality
-    are mainly considered for data prefetching and scheduling policy. Whereas for some complex workloads, the file access pattern 
-    is hard to reveal due to ... 
-    We propose Path2Vec, an embedding approach to transform filenames to vectors, thus allowing further analysis of access patterns. 
-    To evaluate the effectiveness of this mechanism, we implemented a
+    are mainly considered for data prefetching and scheduling policy. Whereas for most real world workloads, the file access pattern 
+    is hard to capture.
 
+    For the goal of deeply and intelligently understanding the I/O access pattern of modern applications, and efficiently optimizing performance of current file systems,
+    we propose a new mechanism to embed file names to vectors, and train a gated recurrent neural network to provide policies for file prefeching and cache replacing.
 \end{abstract}
@@
 \begin{IEEEkeywords}
+    \textit{Distributed File System; File Prefetching; Word Embedding; RNN}
 
@@
 \begin{itemize}
-    \item We propose an approach to embedd the names of files or directories with Skipgram algorithm, 
+    \item We propose an approach to embed the names of files or directories with Skipgram algorithm, 
     mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
     \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
-    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to catch I/O access pattern and encode it with hidden states of the GRU.
+    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to capture I/O access pattern and encode it with hidden states of the GRU.
     We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.
@@
 Since version 3.7, the newly implemented feature \textit{tiring} enables different sotrage types to be used by the same logical volume.
-As fig shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
+As Fig.\ref{fig:tiering} shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
 With fine-tuned prefeching and cache replacing policy, large propotion of I/O requests are forwarded to \textit{hot} bricks, thus significantly decreasing access latency.
-In this case, we can reframe(\textcolor{red}{EDIT}) caching/prefeching optimization tasks to binary classification problems,
-where the objective is to dynamically decide whether a file is \textit{hot} or \textit{cold}.
+In this case, we can reframe caching/prefeching optimization tasks to binary classification problems,
+the objective of which is to dynamically decide whether a file is \textit{hot} or \textit{cold}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{images/tiering}
+\caption{Data tiering in GlusterFS}
+\label{fig:tiering}
+\end{figure}
 
@@
 aiming at mapping natural words to real number vectors based on context provided by specific corpora.
-These mapping mechanisms include neural networks, dimensionality reduction on the word co-occurrence matrix, probabilistic methods etc. \textcolor{blue}{refs}
+These mapping mechanisms include neural networks, dimensionality reduction on the word co-occurrence matrix, probabilistic methods, etc.
 
-The most widely utilized model is \textit{skip-gram algorithm}\cite{SkipGram}, 
-which trains a neural network to predict whether a word is likely to show up near another.
-Given a word vocabulary of size $W$, where a word is identified by $w \in {1,\dots,W}$, 
-and a corpus consists of a sequence of words $w_1, \dots, w_T$, the objective of skip-gram algorithm is to maximize the following log probability:
-\begin{equation}
-\frac{1}{T}\sum_{t=1}^{T}\sum_{-c \leq j \leq c,j \neq 0} \log p(w_{t+j} | w_t),
-\end{equation}
-Where $w_t$ denotes the target word at position $t$ in the training corpus and $c$ is the size of context window.
-A basic definition of $p(w_t+j | w_t)$ is the softmax function:
-\begin{equation}
-%    p(w_O | w_I) = \frac{\exp{v'_{w_O}^{\top}}{b}
-\end{equation}
-However, it's generally impractical to calculate softmax function due to the tremendous \textbf{(EDIT)}computational complexity,
-as the size of vocabulary may be too large.
-To estimate ...
+Among the mechanisms metioned above, the Skip-gram model is an efﬁcient method for learning high-quality distributed vector representations that capture a large number of precise syntactic and semantic word relationships.
+
+%Given a word vocabulary of size $W$, where a word is identified by $w \in {1,\dots,W}$, 
+%and a corpus consists of a sequence of words $w_1, \dots, w_T$, the objective of skip-gram algorithm is to maximize the following log probability:
+%\begin{equation}
+%\frac{1}{T}\sum_{t=1}^{T}\sum_{-c \leq j \leq c,j \neq 0} \log p(w_{t+j} | w_t),
+%\end{equation}
+%Where $w_t$ denotes the target word at position $t$ in the training corpus and $c$ is the size of context window.
+%A basic definition of $p(w_t+j | w_t)$ is the softmax function:
+%\begin{equation}
+%    p(w_O | w_I) = \frac{ \exp( {v'}_{w_O}^{\top} v_{w_I}) }{\sum_{w=1}^W \exp({v'}_w^{\top} v_{w_I})}
+%\end{equation}
+%However, it's generally impractical to calculate softmax function due to the tremendous \textbf{(EDIT)}computational complexity,
+%as the size of vocabulary may be too large.
+%To estimate ...
 
@@
 
-Gated recurrent unit(GRU)\textcolor{blue}{ref} is a gating mechanism in RNNs, 
-which is like a long short-term memory(LSTM)\textcolor{blue}{ref} with forget gate but has fewer parameters.
-See \textcolor{blue}{fig}
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{images/GRU}
+\caption{Gated recurrent unit}
+\end{figure}
+The GRU(gated recurrent unit)\cite{GRU} is a gating mechanism in RNNs, 
+which is like a LSTM(long short-term memory)\cite{LSTM} with forget gate but has fewer parameters.
 
@@
 we assume that these methodologies are suitable in analytics and optimizations for posix file systems as well.
-\textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim(\textcolor{red}{EDIT}) that \textit{a} and \textit{b},
+\textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim that \textit{a} and \textit{b},
 \textit{b} and \textit{c} are parent-child pairs, while \textit{c} and \textit{d} are a pair of brothers with the same parent \textit{b}.
 Or, intuitively, they are logically close to each other in this directory tree. 
-This basic relation is analogous to 2-Grams (\textcolor{red}{EDIT}) in natural language models.
+This basic relation is analogous to 2-Grams model in natural language models.
 
@@
 \subsection{Access Pattern Analytics with Gated Recurrent Neural Network}
-\subsubsection{Data pre-processing}
+\subsubsection{Data Pre-processing}
 To collect file access histories, we insert a trace translator into GlusterFS.
@@
 attemtpting to reveal its underlying access patterns beyond basic locality. 
-As \textbf{fig} illustrated, the components of parameter \textit{path} in each \textit{open} request are transformed to vectors and summed up.\textcolor{red}{edit}
+The components of the \textit{path} in each \textit{open} request are transformed and added up to form a vector.
+e.g., given $i$th accessed path named \textit{/foo/bar/file}, the three components are respectively transformed to three vectors: $\{\mathbf{v}_1, \mathbf{v}_2, \mathbf{v}_3\}$,
+and summed up to form a vector $\mathbf{x}_i = \mathbf{v}_1 + \mathbf{v}_2 + \mathbf{v}_3$.
+Finally, a sequence of vectors $\mathbf{x}=(\mathbf{x_1}, \dots, \mathbf{x_T})$ representing access history of size $T$ are generated.
 
-\textcolor{blue}{A figure here}
-
-Finally, a sequence of vectors $\mathbf{x}=(\mathbf{x_1}, \dots, \mathbf{x_T})$ representing access history of size $T$ have been generated.
-
-\subsubsection{GRU-based model building\textcolor{red}{edit}}
+\subsubsection{GRU-based Model Building}
 In our design, we utilize a single-layer GRU to calculate and update the hidden state, which implicitly represents the access pattern of the target workloads. 
@@
 Where the parameter $\theta = \{W_z, U_z, W, U, W_r, U_r\}$.
-We train this GRU with BPTT(backpropagation through time)\textcolor{red}{ref}.
+We train this GRU with BPTT(backpropagation through time).
 
@@
 \subsection{Experiment and Parameter Settings}
-We choose compiling workloads for experiments and collect a few different repositories from Github,
-including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
+We use a 4 node cluster to build a distributed file system based on GlusterFS. 
+Each node is deployed on a CentOS7 Server virtual machine on the different physical machines connected by Ethernet, 
+and each virtual machine has one CPU, 1G memory and 20G RAM. Each node is equiped with one hard disk as \textit{cold} brick,
+and an SSD driver with volume of 40 GB deployed as the \textit{hot} brick.
+
+We choose compiling workloads as the target, and collect 20 different repositories from Github.
+%including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
 We split these repositories into two groups, 10 arbitrary repositories for training and the others for testing.
 
-To evaluate the performance of our model,
+To evlatuate the performance of our model, we adjust the context window size $N$ for testing. 
+Whereas another hyper parameter, the dimension of the embedded vectors is fixed to be 16. 
+\subsection{Results for Hit Rate and Access Latency Testing}
 
-\subsection{Results}
+\begin{table}[htbp]
+    \caption{Results for hit rate and access latency testing} 
+\begin{center}
+    \begin{tabular}{ |c|c|c| } 
+     \hline
+     \textbf{\textit{Size of}}&\textbf{\textit{Average}} &\textbf{\textit{Average Access}}\\ 
+     \textbf{\textit{Context Window}}& \textbf{\textit{Hit Rate}} & \textbf{\textit{Latency(ms)}}\\
+     \hline
+     \hline
+     0	&0	&270\\
+     \hline
+     50	&0.13	&263\\
+     \hline
+     100	&0.21	&255\\
+     \hline
+     150	&0.26	&242\\
+     \hline
+     200	&0.42	&233\\
+     \hline
+     250	&0.53	&225\\
+     \hline
+     300	&0.66	&221\\
+     \hline
+     350	&0.77	&207\\
+     \hline
+     400	&0.74	&218\\
+     \hline
+     450	&0.7	&231\\
+     \hline
+     500	&0.67	&245\\
+     \hline
+    \end{tabular}
+\end{center}
 
+%    The first line of data refer to the baseline, where the size of context window is set to 0, 
+%    that means our prefetching mechanism does not work.}
+    \label{table:result}
+\end{table}
+As shown in Table. \ref{table:result}, where the first line of data refers to the baseline, i.e., the model and the prefeching mechanism do not work.
+We can conclude that our mechanism bring benifits to the file system compared to no-prefeching state.
+From Fig.~\ref{fig:hit_rate} and Fig.~\ref{fig:latency}, we can clearly observe that this profit brought by our mechanism is limited, 
+due to the increasing tradeoff when the context window is enlarging.
+\begin{figure}
+\centering
+\includegraphics[width=.5\textwidth]{images/hit_rate}
+\caption{Hit rate testing}
+\label{fig:hit_rate}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.5\textwidth]{images/latency}
+\caption{Access latency testing}
+\label{fig:latency}
+\end{figure}
 %\subsection{\textcolor{red}{EDIT}Similarity Experiment for Directory/File Names}
@@
 
-There are several works to accomplish in the future. First, the model should be deployed in tiering translator in GlusterFS,
-thus making it possible to exploit our model in real fils system for optimization purpose. 
-Also, our work should be scaled to more real world workloads rather than compiling.
+There are several works to accomplish in the future. First, the size of context window should be adaptive to the volume of the cache, 
+as well as the CPU resources of the storage nodes.
+Also, our work should be scaled to serve more real world workloads rather than single process applications like compiling, 
+especially for scientific workloads in exscale parallel computing and cloud computing circumstances.
 \bibliographystyle{plain}

### 2019-09-18 master/paper.tex
9.18

@@
     depends on the understanding of the I/O behavior. Traditionally, spatial locality and temporal locality
-    are mainly considered for data prefetching and scheduling policy. Whereas for most real world workloads, the file access pattern 
+    are mainly considered for data prefetching and scheduling policy. Whereas for most real-world workloads, the file access pattern 
     is hard to capture.
 
-    For the goal of deeply and intelligently understanding the I/O access pattern of modern applications, and efficiently optimizing performance of current file systems,
-    we propose a new mechanism to embed file names to vectors, and train a gated recurrent neural network to provide policies for file prefeching and cache replacing.
+    For the goal of deeply and intelligently understanding the I/O access pattern of modern applications, and efficiently optimizing the performance of current file systems,
+    we propose a new mechanism to embed file names to vectors and train a gated recurrent neural network to provide policies for file prefeching and cache replacing.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-    \textit{Distributed File System; File Prefetching; Word Embedding; RNN}
+    Distributed File System, File Prefetching, Word Embedding, RNN
 
@@
 with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
-In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
-Caches with high throughput and low latency devices like non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.
+To narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
+Caches with high throughput and low latency devices like non-volatile memories(NVMs) and solid-state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.
 
-For purpose of caching data from lower storage in predictable manner, access pattern detection is essential.
+To cache data from lower storage in a predictable manner, access pattern detection is essential.
 Traditionally, spatial locality and temporal locality are most generally considered facts. 
-\textit{Readahead} is a basic mechanism implemented by most file systems\cite{WhyDoes} including linux kernel, which prefeches constant size of data from a opened file to the cache. 
-For workloads excuting sequential read, this approach benefits a lot due to the simple and definite pattern.
-Unfortunately, many applications especially sientific ones usually do not access files sequentially.
+\textit{Readahead} is a basic mechanism implemented by most file systems\cite{WhyDoes} including Linux kernel, which prefetches constant size of data from an opened file to the cache. 
+For workloads executing sequential read, this approach benefits a lot due to the simple and definite pattern.
+Unfortunately, many applications especially scientific ones usually do not access files sequentially.
 
-The main contributions of this paper can be summerized as follow.
+The main contributions of this paper can be summarized as follow.
 \begin{itemize}
@@
     mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
-    \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
+    \item To collect I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
     \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to capture I/O access pattern and encode it with hidden states of the GRU.
-    We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.
+    We combine the hidden states with file vectors to build a file classifier, which dynamically decides whether a file should be cached or purged from the cache.
 
@@
 \section{Related Work}
-The I/O subsystem is becoming the bottleneck of high performance distributed systems, 
-especially there are many communication intensive applications in them \cite{Related_Network_I/O_load_based}.
+The I/O subsystem is becoming the bottleneck of high-performance distributed systems, 
+especially there are many communication-intensive applications in them \cite{Related_Network_I/O_load_based}.
 In order to achieve potential performance enhancements of storage systems, 
@@
 \cite{Related_Multi_Layer_Event_Trace_Analysis} \cite{Related_Towards_an_I/O_tracing_framework_taxonomy} \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related} \cite{Scalable_IO_Tracing_Related}.
-However, existing approaches including aforementioned ones have mostly focused on classifying I/O access patterns by analyzing either the history of applications’ I/O requests
+However, existing approaches including the aforementioned ones have mostly focused on classifying I/O access patterns by analyzing either the history of applications’ I/O requests
 \cite{Parallel_IO_Prefetching_Related} \cite{Learning_To_Classify_Related}
 or the track of block access events \cite{Related_DiskSeen} \cite{A_Prefetching_Scheme_Related}, 
-so that the analyzed results can be used for directing I/O optimization strategies, such as data prefetching.
+so that the analyzed results can be used for direct I/O optimization strategies, such as data prefetching.
 The mechanism of data prefetching focuses on how to forecast future possible read requests, and thus, 
@@
 
-There is a wide range of sophisticated approaches to fulﬁll data prefetching, 
+There is a wide range of sophisticated approaches to fulfill data prefetching, 
 which utilize hidden Markov models, 
@@
 \subsection{Introduction to GlusterFS}
-GlusterFS is a scalable distributed filesystem which is suitable for data-intensive workloads such as cloud storage and high performance computing.
+GlusterFS is a scalable distributed filesystem which is suitable for data-intensive workloads such as cloud storage and high-performance computing.
 It aggregates various storage servers over Ethernet or Infiniband RDMA interconnect into one large parallel network file system.
@@
 
-Since version 3.7, the newly implemented feature \textit{tiring} enables different sotrage types to be used by the same logical volume.
+Since version 3.7, the newly implemented feature \textit{tiring} enables different storage types to be used by the same logical volume.
 As Fig.\ref{fig:tiering} shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
-With fine-tuned prefeching and cache replacing policy, large propotion of I/O requests are forwarded to \textit{hot} bricks, thus significantly decreasing access latency.
+With fine-tuned prefeching and cache replacing policy, a large proportion of I/O requests are forwarded to the \textit{hot} bricks, thus significantly decreasing access latency.
 In this case, we can reframe caching/prefeching optimization tasks to binary classification problems,
@@
 
-Among the mechanisms metioned above, the Skip-gram model is an efﬁcient method for learning high-quality distributed vector representations that capture a large number of precise syntactic and semantic word relationships.
+Among the mechanisms mentioned above, the Skip-gram model is an efficient method for learning high-quality distributed vector representations that capture a large number of precise syntactic and semantic word relationships.
 
@@
 \subsection{Gated Recurrent Neural Networks}
-RNNs(\textit{Recurrent Neural Networks}) have been widely utilized and shown exellent performance in multiple NLP tasks,
-such as speech recognition, machine translation and text emotion classification etc.
-The RNN is an extension of a conventional feedforward neural network, which is able to process a variable-length sequence input.
+RNNs(\textit{Recurrent Neural Networks}) have been widely utilized and shown excellent performance in multiple NLP tasks,
+such as speech recognition, machine translation, and text emotion classification, etc.
+The RNN is an extension of a conventional feedforward neural network, which can process a variable-length sequence input.
 Given a sequence input $x = (x_1, x_2, \dots, x_T)$, the RNN updates its recurrent hidden state $h_t$ by
@@
 The GRU(gated recurrent unit)\cite{GRU} is a gating mechanism in RNNs, 
-which is like a LSTM(long short-term memory)\cite{LSTM} with forget gate but has fewer parameters.
+which is like an LSTM(Long Short-Term Memory)\cite{LSTM} with forget gate but has fewer parameters.
 
@@
 \subsection{Path Embedding Model}
-Since words embedding mechanisms have significantly promoted the performance of plenty of NLP tasks, 
-we assume that these methodologies are suitable in analytics and optimizations for posix file systems as well.
+Since word embedding mechanisms have significantly promoted the performance of plenty of NLP tasks, 
+we assume that these methodologies are suitable in analytics and optimizations for POSIX file systems as well.
 \textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim that \textit{a} and \textit{b},
@@
 it is assumed that the naming conventions and directory structure are regularly formed by producers or users.
-Thus it is possible to form a vocabulary and train an embedding model to represent each directory/file name as a vector.
+Thus it is possible to form vocabulary and train an embedding model to represent each filename as a vector.
 
-To generate corpora for training purpose,
-we recursively traverse the target directory from root entry and print the paths into a txt file line by line.
-After that, the Skip-gram algorithm is invoked to train a embedding model, 
-which finally provides a vocabulary for all the occured directory/file names and a table consists of vectors for these names.
+To generate corpora for training purposes,
+we recursively traverse the target directory from root entry and print the paths into a text file line by line.
+After that, the Skip-gram algorithm is invoked to train an embedding model, 
+which finally provides a vocabulary for all the occurred directory/file names and a table consists of vectors for these names.
 
@@
 To collect file access histories, we insert a trace translator into GlusterFS.
-So far, we mainly focus on file \textit{open} operation in order to detect when, how and what files does the workload start to access during its lifetime,
-attemtpting to reveal its underlying access patterns beyond basic locality. 
+So far, we mainly focus on file \textit{open} operation to detect when, how and what files does the workload starts to access during its lifetime,
+attempting to reveal its underlying access patterns beyond the basic locality. 
 The components of the \textit{path} in each \textit{open} request are transformed and added up to form a vector.
-e.g., given $i$th accessed path named \textit{/foo/bar/file}, the three components are respectively transformed to three vectors: $\{\mathbf{v}_1, \mathbf{v}_2, \mathbf{v}_3\}$,
+e.g., given $i$th accessed path named \textit{/foo/bar/file}, the three components are respectively transformed into three vectors: $\{\mathbf{v}_1, \mathbf{v}_2, \mathbf{v}_3\}$,
 and summed up to form a vector $\mathbf{x}_i = \mathbf{v}_1 + \mathbf{v}_2 + \mathbf{v}_3$.
@@
 In our design, we utilize a single-layer GRU to calculate and update the hidden state, which implicitly represents the access pattern of the target workloads. 
-Given dataset $\mathbf{x} = (\mathbf{x}_1,\dots,\mathbf{x}_T)$ representing a sequence of file access history excuted by the target workload, 
+Given dataset $\mathbf{x} = (\mathbf{x}_1,\dots,\mathbf{x}_T)$ representing a sequence of file access history executed by the target workload, 
 we take these vectors as input sequence for the GRU and train the model.
@@
 \end{equation}
-The candidate acitivation $\tilde{h}_t^{(j)}$ is computed by:
+The candidate activation $\tilde{h}_t^{(j)}$ is computed by:
 \begin{equation}
@@
 \end{equation}
-Where $\mathbf{r}_t$ are \textit{reset gates} and $\odot$ is a pointwise multiplication(Hadarmard product).
+Where $\mathbf{r}_t$ are \textit{reset gates} and $\odot$ is a pointwise multiplication(Hadamard product).
 The reset gate is calculated by
@@
 \end{equation}
-For purpose of discriminating files between \textit{hot} and \textit{cold}, 
-our goal is to train the GRU to provide appropriate hidden states for classification. 
+To discriminate files between \textit{hot} and \textit{cold}, 
+our goal is to train the GRU to provide hidden states for classification. 
 We denote $N$ as the approximation of the number of files fit in the cache,
@@
 Where the parameter $\theta = \{W_z, U_z, W, U, W_r, U_r\}$.
-We train this GRU with BPTT(backpropagation through time).
+We train this GRU with BPTT(Backpropagation Through Time).
 
@@
 We use a 4 node cluster to build a distributed file system based on GlusterFS. 
-Each node is deployed on a CentOS7 Server virtual machine on the different physical machines connected by Ethernet, 
-and each virtual machine has one CPU, 1G memory and 20G RAM. Each node is equiped with one hard disk as \textit{cold} brick,
-and an SSD driver with volume of 40 GB deployed as the \textit{hot} brick.
+Each node is deployed on a CentOS7 Server virtual machine on the different physical machines connected by Ethernet
+and each virtual machine has one CPU, 1G memory and 20G RAM. Each node is equipped with a hard disk as \textit{cold} brick,
+and an SSD with a volume of 40 GB deployed as the \textit{hot} brick.
 
-We choose compiling workloads as the target, and collect 20 different repositories from Github.
+We choose compiling workloads as the target and collect 20 different repositories from Github.
 %including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
@@
 
-To evlatuate the performance of our model, we adjust the context window size $N$ for testing. 
-Whereas another hyper parameter, the dimension of the embedded vectors is fixed to be 16. 
+To evaluate the performance of our model, we adjust the context window size $N$ for testing. 
+Whereas another hyperparameter, the dimension of the embedded vectors is fixed to be 16. 
 \subsection{Results for Hit Rate and Access Latency Testing}
@@
 As shown in Table. \ref{table:result}, where the first line of data refers to the baseline, i.e., the model and the prefeching mechanism do not work.
-We can conclude that our mechanism bring benifits to the file system compared to no-prefeching state.
-From Fig.~\ref{fig:hit_rate} and Fig.~\ref{fig:latency}, we can clearly observe that this profit brought by our mechanism is limited, 
+We can conclude that our mechanism brings benifits to the file system compared to the non-prefeching state.
+From Fig.~\ref{fig:hit_rate} and Fig.~\ref{fig:latency}, we can observe that this profit brought by our mechanism is limited, 
 due to the increasing tradeoff when the context window is enlarging.
@@
 \section{Conclusion}
-In this paper, we systematically discuss the similarity between natural language processing and posix file systems,
-and propose a new approach to represent posix file/direcory names with Skip-gram algorithm. 
+In this paper, we systematically discuss the similarity between natural language processing and POSIX file systems,
+and propose a new approach to represent POSIX file/directory names with the Skip-gram algorithm. 
 With this embedding mechanism, we map the file/directory names into a high dimension vector space, 
-where the relation between files can be dipicted by dot production of these two vectors.
+where the relation between files can be depicted by the dot production of these two vectors.
 
 Based on this embedding mechanism, we exploit a single-layer GRNN(Gated Recurrent Neural Network) taking file access history as sequence input.
-With well trained GRU, we are able to encode the access pattern to the hidden state and dynamically decide whether a file is \textit{hot} or \textit{cold},
+With well trained GRU, we can encode the access pattern to the hidden state and dynamically decide whether a file is \textit{hot} or \textit{cold},
 thus providing hints for caching/prefeching and cache replacing policies.
 
-There are several works to accomplish in the future. First, the size of context window should be adaptive to the volume of the cache, 
+There are several works to accomplish in the future. First, the size of the context window should be adaptive to the volume of the cache, 
 as well as the CPU resources of the storage nodes.
-Also, our work should be scaled to serve more real world workloads rather than single process applications like compiling, 
-especially for scientific workloads in exscale parallel computing and cloud computing circumstances.
+Also, our work should be scaled to serve more real-world workloads rather than single-process applications like compiling, 
+especially for scientific workloads in exascale parallel computing and cloud computing circumstances.
 \bibliographystyle{plain}

### 2020-01-23 Templates/presentations/p1.tex
"push"

\documentclass{beamer}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{unicode-math}
\usepackage{verbatim}
\usepackage{xeCJK}
\mode<presentation> {
\setbeamertemplate{footline}[frame number]
\beamertemplatenavigationsymbolsempty
% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Short title]{标题} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{John Smith} % Your name
\institute[UCLA] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
University of California \\ % Your institution for the title page
\medskip
\textit{john@smith.com} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{测试} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{中文} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Paragraphs of Text}
Sed iaculis dapibus gravida. Morbi sed tortor erat, nec interdum arcu. Sed id lorem lectus. Quisque viverra augue id sem ornare non aliquam nibh tristique. Aenean in ligula nisl. Nulla sed tellus ipsum. Donec vestibulum ligula non lorem vulputate fermentum accumsan neque mollis.\\~\\

Sed diam enim, sagittis nec condimentum sit amet, ullamcorper sit amet libero. Aliquam vel dui orci, a porta odio. Nullam id suscipit ipsum. Aenean lobortis commodo sem, ut commodo leo gravida vitae. Pellentesque vehicula ante iaculis arcu pretium rutrum eget sit amet purus. Integer ornare nulla quis neque ultrices lobortis. Vestibulum ultrices tincidunt libero, quis commodo erat ullamcorper id.
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Bullet Points}
\begin{itemize}
\item Lorem ipsum dolor sit amet, consectetur adipiscing elit
\item Aliquam blandit faucibus nisi, sit amet dapibus enim tempus eu
\item Nulla commodo, erat quis gravida posuere, elit lacus lobortis est, quis porttitor odio mauris at libero
\item Nam cursus est eget velit posuere pellentesque
\item Vestibulum faucibus velit a augue condimentum quis convallis nulla gravida
\end{itemize}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Blocks of Highlighted Text}
\begin{block}{Block 1}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Integer lectus nisl, ultricies in feugiat rutrum, porttitor sit amet augue. Aliquam ut tortor mauris. Sed volutpat ante purus, quis accumsan dolor.
\end{block}

\begin{block}{Block 2}
Pellentesque sed tellus purus. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Vestibulum quis magna at risus dictum tempor eu vitae velit.
\end{block}

\begin{block}{Block 3}
Suspendisse tincidunt sagittis gravida. Curabitur condimentum, enim sed venenatis rutrum, ipsum neque consectetur orci, sed blandit justo nisi ac lacus.
\end{block}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Multiple Columns}
\begin{columns}[c] % The "c" option specifies centered vertical alignment while the "t" option is used for top vertical alignment

\column{.45\textwidth} % Left column and width
\textbf{Heading}
\begin{enumerate}
\item Statement
\item Explanation
\item Example
\end{enumerate}

\column{.5\textwidth} % Right column and width
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Integer lectus nisl, ultricies in feugiat rutrum, porttitor sit amet augue. Aliquam ut tortor mauris. Sed volutpat ante purus, quis accumsan dolor.

\end{columns}
\end{frame}

%------------------------------------------------
\section{Second Section}
%------------------------------------------------

\begin{frame}
\frametitle{Table}
\begin{table}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Theorem}
\begin{theorem}[Mass--energy equivalence]
$E = mc^2$
\end{theorem}
\end{frame}

%------------------------------------------------

\begin{frame}[fragile] % Need to use the fragile option when verbatim is used in the slide
\frametitle{Verbatim}
\begin{example}[Theorem Slide Code]
\begin{verbatim}
\begin{frame}
\frametitle{Theorem}
\begin{theorem}[Mass--energy equivalence]
$E = mc^2$
\end{theorem}
\end{frame}\end{verbatim}
\end{example}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Figure}
Uncomment the code on this slide to include your own image from the same directory as the template .TeX file.
%\begin{figure}
%\includegraphics[width=0.8\linewidth]{test}
%\end{figure}
\end{frame}

%------------------------------------------------

\begin{frame}[fragile] % Need to use the fragile option when verbatim is used in the slide
\frametitle{Citation}
An example of the \verb|\cite| command to cite within the presentation:\\~

This statement requires citation \cite{p1}.
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{References}
\footnotesize{
\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
\bibitem[Smith, 2012]{p1} John Smith (2012)
\newblock Title of the publication
\newblock \emph{Journal Name} 12(3), 45 -- 678.
\end{thebibliography}
}
\end{frame}

%------------------------------------------------

\begin{frame}
\Huge{\centerline{The End}}
\end{frame}

%----------------------------------------------------------------------------------------

\end{document}
